---
title: "Assignment 1.6"
subtitle: "CPSC 292 Section #1 (Waldrop)"
author: "Raina Hirekatur"
date: "09/08/2023"
output: html_notebook
---

### Collaboration team: 

Record who you've worked on the assignment with here: Jesille, Victoria


## Assignment 1.6 -- Data Types in R

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*For the following inputs, list all of the data type(s) that would be appropriate to store data in R. Code the example for each.*

  a. *The word fart*
  
  Your answer here: Character
```{r}
my_word <- c("fart")
print(my_word)
class(my_word)
```
  b. *The condition TRUE*
  
  Your answer here: Logical
```{r}
l <- c(TRUE)
```
  c. *The vector < FALSE, TRUE, FALSE, FALSE, TRUE >*
  
  Your answer here: Logical
```{r}
l1 <- c(FALSE,TRUE,FALSE,FALSE,TRUE)
```
  d. *The vector < 1, 0, 1, 0 >*
  
  Your answer here: Integer & Numeric
```{r}
i <- c(1L, 0L, 1L, 0L)
```
  e. *The vector < 2.66, 2.66 >*
  
  Your answer here: Numeric
```{r}
n <- c(2.66, 2.66)
```
  f. *The vector < 2i, 3+3i >*
  
  Your answer here: Complex
```{r}
c <- c(2i, 3+3i)
```
  g. *The number 8*
  
  Your answer here: Integer
```{r}
i2 <- c(8)
```
  h. *The number 3.6*

  Your answer here: Numeric
```{r}
n2 <- c(3.6)
```

### Question 2

*For the following functions, what types of data do they accept as inputs and what data types do they return as outputs? Code a working example of each.*

 a. `median()`
  
```{r}
median(c(5, 8, 2, 10, 6))
#Inputs: numeric, integer, logical, factors, data frames, lists
#Outputs: numeric, integer, logical, factors, data frames, lists
```

 b. `sd()`
 
```{r}
sd(c(5, 8, 2, 10, 6))
#Inputs: numeric, integer, logical, factors, data frames, lists
#Outputs: numeric
```
 
 c. `any()`
   
```{r}
any(T,F,T,T)
#Inputs: logical
#Outputs:logical
```
 
 d. `cut()`
 
```{r}
age <- c(12,23,34,47,58,59,62,79)
age_break <- c(0,10,20,30,40,50,60,70, max(age))
age_label <- c("<20", "10-19","20-29", "30-39", "40-49", "50-59", "60-69", "70+")
age_group <- cut(age, breaks = age_break, labels = age_label, right = TRUE)
#Inputs: numeric, breaks, labels, right
#Outputs: factor, numeric
```
 
 e. `order()`
  
```{r}
order(c(5, 8, 2, 10, 6))
#Inputs: numeric, character
#Outputs:integer
```

### Question 3

*Run the function `is.character()` on the coded example for each answer in question 1 (give each example
its own line). What does the output mean?*

```{r}
is.character(my_word)
is.character(TRUE)
is.character(FALSE)
is.character(1L)
is.character(2.66)
is.character(3+3i)
is.character(8)
is.character(3.6)
```

Your answer here. 

### Question 4

*Use the function `runif()` to produce 1000 random numbers between 0 and 1.*

```{r}
runif(1000, min = 0, max =1)
```

*How could you change the range from 10 to 1000 (instead of 0 to 1)? Write an explanation here describing the change and then put the adjusted code.*

Your answer here.

```{r}
runif(1000, min = 10, max =100)
#you need to adjust the min and max values according to what values you want the output of
```



Turn in this RMD file.